---
title: "Analysis: Part 1a"
author: 
date: '`r format(Sys.Date(), "%B %d, %Y")`'
geometry: margin=1in
output: 
  pdf_document:
    number_sections: TRUE
---


```{r global_options, include=FALSE}
knitr::opts_chunk$set(tidy = TRUE)
knitr::opts_chunk$set(fig.pos = 'H')
```


```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(rmarkdown)
library(knitr)
library(kableExtra)
```


```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(dplyr)
library(geeM)
path_output_data <- Sys.getenv("path_output_data")

# Read in functions for data analysis
source("analysis-utils.R")

# Read in data
dat_baseline_analysis <- read.csv(file.path(path_output_data, "dat_baseline_analysis.csv"), header = TRUE)
dat_screener_analysis <- read.csv(file.path(path_output_data, "dat_screener_analysis.csv"), header = TRUE)
dat_wnw_analysis <- read.csv(file.path(path_output_data, "dat_wnw_analysis.csv"), header = TRUE)

# Center and scale variables
dat_baseline_analysis <- dat_baseline_analysis %>% mutate(across(!c("ParticipantID"), scale))
dat_screener_analysis <- dat_screener_analysis %>% mutate(across(!c("ParticipantID","sex","race"), scale))
dat_wnw_analysis_0 <- dat_wnw_analysis %>% filter(time==0) %>% mutate(across(!c("ParticipantID","time","survey_timepoint","CASEID","HED","rutgers"), scale))
dat_wnw_analysis_1 <- dat_wnw_analysis %>% filter(time==1) %>% mutate(across(!c("ParticipantID","time","survey_timepoint","CASEID","HED","rutgers"), scale))
dat_wnw_analysis <- rbind(dat_wnw_analysis_0, dat_wnw_analysis_1)
dat_wnw_analysis <- dat_wnw_analysis %>% arrange(ParticipantID, time)
remove(dat_wnw_analysis_0, dat_wnw_analysis_1)

# Merge datasets into one data frame
dat_analysis <- left_join(x = dat_wnw_analysis, y = dat_screener_analysis, by = "ParticipantID")
dat_analysis <- left_join(x = dat_analysis, y = dat_baseline_analysis, by = "ParticipantID")
dat_analysis <- dat_analysis %>% select(colnames(dat_screener_analysis), colnames(dat_baseline_analysis), everything())
```

# Hypotheses

(H1a): More permissive peer drinking norms are associated with an increase in alcohol misuse among young adults transitioning from college to work

(H4) The effect of drinking norms on alcohol misuse intensifies over time: It is stronger during the late onboarding phase than the early onboarding phase.

(H5): During the early onboarding phase, the effect of peer drinking norms on employee alcohol misuse is moderated by psychological distress such that its effect on alcohol misuse is attenuated as a function of psychological distress.


# Drinking Norms Variables

* Perceived injunctive work place drinking norms: mean of wnw111 and wnw114

* Perceived descriptive work place drinking norms: mean of wnw116 and wnw117

| wnw111 | wnw114 | wnw116 | wnw117 |
|:-------------:|:-------------:|:-------------:|:-------------:|
| Please indicate the degree to which these others, not you, disapprove/approve of the various patterns of alcohol consumption described. What is the extent you believe: Your closest friends at work would approve/disapprove were you to have 1-2 servings of alcohol within an hour of coming to work?  | Please indicate the degree to which these others, not you, disapprove/approve of the various patterns of alcohol consumption described. What is the extent you believe: Your closest friends and colleagues at work would approve/disapprove were you to have 1-2 servings of alcohol at work? | In the past month, how many of your closest friends and colleagues at work: Consumed 1-2 servings of alcohol within an hour before starting work? | In the past month, how many of your closest friends and colleagues at work: Consumed at least one serving of alcohol during the work day? | 
| **1: Disapprove very much; 5: Approve very much **| **1: Disapprove very much; 5: Approve very much** | **1: None; 5: All** | **1: None; 5: All** |


\newpage
# Outcome: RAPI

## Injunctive Drinking Norms

```{r, echo = FALSE, message = FALSE, warning = FALSE}
fit_rutgers_1 <- geem(rutgers ~ sex + race + age + baseline_rutgers + baseline_social_desirability + baseline_impulsivity + lifestress 
                      + injunctive_workplace_norms, 
                  data = dat_analysis, id = ParticipantID, waves = time, corstr = "exchangeable", family = "quasipoisson")

outfit_rutgers_1 <- FormatGEEOutput(fit_rutgers_1)
N_rutgers_1 <- length(setdiff(unique(dat_analysis$ParticipantID), fit_rutgers_1$dropped))
```


```{r, echo = FALSE, message = FALSE, warning = FALSE}
fit_rutgers_2 <- geem(rutgers ~ sex + race + age + baseline_rutgers + baseline_social_desirability + baseline_impulsivity + lifestress
                     + time + injunctive_workplace_norms + injunctive_workplace_norms:time, 
                  data = dat_analysis, id = ParticipantID, waves = time, corstr = "exchangeable", family = "quasipoisson")

outfit_rutgers_2 <- FormatGEEOutput(fit_rutgers_2)
N_rutgers_2 <- length(setdiff(unique(dat_analysis$ParticipantID), fit_rutgers_2$dropped))
```


```{r, echo = FALSE, message = FALSE, warning = FALSE}
fit_rutgers_3 <- geem(rutgers ~ sex + race + age 
                                + baseline_rutgers + baseline_social_desirability + baseline_impulsivity + lifestress
                                + time + injunctive_workplace_norms + DASS + injunctive_workplace_norms:DASS
                                + injunctive_workplace_norms:time + DASS:time + injunctive_workplace_norms:DASS:time, 
                  data = dat_analysis, id = ParticipantID, waves = time, corstr = "exchangeable", family = "quasipoisson")

outfit_rutgers_3 <- FormatGEEOutput(fit_rutgers_3)
N_rutgers_3 <- length(setdiff(unique(dat_analysis$ParticipantID), fit_rutgers_3$dropped))

# Calculate effects at early onboarding phase
Lmat_low <- as.matrix(c(0,0,0,0, # intercept, sex, race, age
                        0,0,0,0, # end with lifestress
                        # END: control variables
                        0,1,0,-1,
                        0,0,0))

Lmat_mod <- as.matrix(c(0,0,0,0, # intercept, sex, race, age
                        0,0,0,0, # end with lifestress
                        # END: control variables
                        0,1,0,0,
                        0,0,0))

Lmat_hig <- as.matrix(c(0,0,0,0, # intercept, sex, race, age
                        0,0,0,0, # end with lifestress
                        # END: control variables
                        0,1,0,1,
                        0,0,0))

Lmat_low <- t(Lmat_low)
Lmat_mod <- t(Lmat_mod)
Lmat_hig <- t(Lmat_hig)

ss_low <- GetSS(use_this_model = fit_rutgers_3, L = Lmat_low)
ss_mod <- GetSS(use_this_model = fit_rutgers_3, L = Lmat_mod)
ss_hig <- GetSS(use_this_model = fit_rutgers_3, L = Lmat_hig)

ss_tab <- rbind(ss_low, ss_mod, ss_hig)
row.names(ss_tab) <- c("At early onboarding phase: effect of norms at low DASS",
                       "At early onboarding phase: effect of norms at moderate DASS",
                       "At early onboarding phase: effect of norms at high DASS")
```


```{r, echo = FALSE, message = FALSE, warning = FALSE}
outfit_rutgers_1 %>%
  mutate(parameter = as.character(row.names(.))) %>%
  mutate(parameter = gsub("_"," ", .data[["parameter"]])) %>%
  mutate(parameter = gsub(":"," x ", .data[["parameter"]])) %>%
  select(parameter, everything()) %>%
  mutate_all(linebreak) %>%
  kable(booktabs = TRUE, align = c('c','c','c','c'),
        col.names = linebreak(c("Parameter","Estimates","SE","p-value"), align = "c"),
        caption = paste("Outcome: Rutgers Alcohol Problem Index; N = ", N_rutgers_1, sep=""), escape = FALSE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD_position"))  

outfit_rutgers_2 %>%
  mutate(parameter = as.character(row.names(.))) %>%
  select(parameter, everything()) %>%
  mutate(parameter = gsub("_"," ", .data[["parameter"]])) %>%
  mutate(parameter = gsub(":"," x ", .data[["parameter"]])) %>%
  mutate_all(linebreak) %>%
  kable(booktabs = TRUE, align = c('c','c','c','c'),
        col.names = linebreak(c("Parameter","Estimates","SE","p-value"), align = "c"),
        caption = paste("Outcome: Rutgers Alcohol Problem Index; N = ", N_rutgers_2, sep=""), escape = FALSE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD_position"))  

outfit_rutgers_3 %>%
  mutate(parameter = as.character(row.names(.))) %>%
  select(parameter, everything()) %>%
  mutate(parameter = gsub("_"," ", .data[["parameter"]])) %>%
  mutate(parameter = gsub(":"," x ", .data[["parameter"]])) %>%
  mutate_all(linebreak) %>%
  kable(booktabs = TRUE, align = c('c','c','c','c'),
        col.names = linebreak(c("Parameter","Estimates","SE","p-value"), align = "c"),
        caption = paste("Outcome: Rutgers Alcohol Problem Index; N = ", N_rutgers_3, sep=""), escape = FALSE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD_position"))  

ss_tab %>%
  mutate(parameter = as.character(row.names(.))) %>%
  select(parameter, everything()) %>%
  kable(booktabs = TRUE, align = c('c','c','c','c','c','c','c'), caption = paste("Outcome: Rutgers Alcohol Problem Index; N = ", N_rutgers_3, sep="")) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD_position", "scale_down"))  
```



\newpage
## Descriptive Drinking Norms

```{r, echo = FALSE, message = FALSE, warning = FALSE}
fit_rutgers_1 <- geem(rutgers ~ sex + race + age + baseline_rutgers + baseline_social_desirability + baseline_impulsivity + lifestress 
                      + descriptive_workplace_norms, 
                  data = dat_analysis, id = ParticipantID, waves = time, corstr = "exchangeable", family = "quasipoisson")

outfit_rutgers_1 <- FormatGEEOutput(fit_rutgers_1)
N_rutgers_1 <- length(setdiff(unique(dat_analysis$ParticipantID), fit_rutgers_1$dropped))
```

```{r, echo = FALSE, message = FALSE, warning = FALSE}
fit_rutgers_2 <- geem(rutgers ~ sex + race + age + baseline_rutgers + baseline_social_desirability + baseline_impulsivity + lifestress
                     + time + descriptive_workplace_norms + descriptive_workplace_norms:time, 
                  data = dat_analysis, id = ParticipantID, waves = time, corstr = "exchangeable", family = "quasipoisson")

outfit_rutgers_2 <- FormatGEEOutput(fit_rutgers_2)
N_rutgers_2 <- length(setdiff(unique(dat_analysis$ParticipantID), fit_rutgers_2$dropped))
```


```{r, echo = FALSE, message = FALSE, warning = FALSE}
fit_rutgers_3 <- geem(rutgers ~ sex + race + age 
                                + baseline_rutgers + baseline_social_desirability + baseline_impulsivity + lifestress
                                + time + descriptive_workplace_norms + DASS + descriptive_workplace_norms:DASS
                                + descriptive_workplace_norms:time + DASS:time + descriptive_workplace_norms:DASS:time, 
                  data = dat_analysis, id = ParticipantID, waves = time, corstr = "exchangeable", family = "quasipoisson")

outfit_rutgers_3 <- FormatGEEOutput(fit_rutgers_3)
N_rutgers_3 <- length(setdiff(unique(dat_analysis$ParticipantID), fit_rutgers_3$dropped))

# Calculate effects at early onboarding phase
Lmat_low <- as.matrix(c(0,0,0,0, # intercept, sex, race, age
                        0,0,0,0, # end with lifestress
                        # END: control variables
                        0,1,0,-1,
                        0,0,0))

Lmat_mod <- as.matrix(c(0,0,0,0, # intercept, sex, race, age
                        0,0,0,0, # end with lifestress
                        # END: control variables
                        0,1,0,0,
                        0,0,0))

Lmat_hig <- as.matrix(c(0,0,0,0, # intercept, sex, race, age
                        0,0,0,0, # end with lifestress
                        # END: control variables
                        0,1,0,1,
                        0,0,0))

Lmat_low <- t(Lmat_low)
Lmat_mod <- t(Lmat_mod)
Lmat_hig <- t(Lmat_hig)

ss_low <- GetSS(use_this_model = fit_rutgers_3, L = Lmat_low)
ss_mod <- GetSS(use_this_model = fit_rutgers_3, L = Lmat_mod)
ss_hig <- GetSS(use_this_model = fit_rutgers_3, L = Lmat_hig)

ss_tab <- rbind(ss_low, ss_mod, ss_hig)
row.names(ss_tab) <- c("At early onboarding phase: effect of norms at low DASS",
                       "At early onboarding phase: effect of norms at moderate DASS",
                       "At early onboarding phase: effect of norms at high DASS")
```


```{r, echo = FALSE, message = FALSE, warning = FALSE}
outfit_rutgers_1 %>%
  mutate(parameter = as.character(row.names(.))) %>%
  mutate(parameter = gsub("_"," ", .data[["parameter"]])) %>%
  mutate(parameter = gsub(":"," x ", .data[["parameter"]])) %>%
  select(parameter, everything()) %>%
  mutate_all(linebreak) %>%
  kable(booktabs = TRUE, align = c('c','c','c','c'),
        col.names = linebreak(c("Parameter","Estimates","SE","p-value"), align = "c"),
        caption = paste("Outcome: Rutgers Alcohol Problem Index; N = ", N_rutgers_1, sep=""), escape = FALSE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD_position"))  

outfit_rutgers_2 %>%
  mutate(parameter = as.character(row.names(.))) %>%
  select(parameter, everything()) %>%
  mutate(parameter = gsub("_"," ", .data[["parameter"]])) %>%
  mutate(parameter = gsub(":"," x ", .data[["parameter"]])) %>%
  mutate_all(linebreak) %>%
  kable(booktabs = TRUE, align = c('c','c','c','c'),
        col.names = linebreak(c("Parameter","Estimates","SE","p-value"), align = "c"),
        caption = paste("Outcome: Rutgers Alcohol Problem Index; N = ", N_rutgers_2, sep=""), escape = FALSE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD_position"))  

outfit_rutgers_3 %>%
  mutate(parameter = as.character(row.names(.))) %>%
  select(parameter, everything()) %>%
  mutate(parameter = gsub("_"," ", .data[["parameter"]])) %>%
  mutate(parameter = gsub(":"," x ", .data[["parameter"]])) %>%
  mutate_all(linebreak) %>%
  kable(booktabs = TRUE, align = c('c','c','c','c'),
        col.names = linebreak(c("Parameter","Estimates","SE","p-value"), align = "c"),
        caption = paste("Outcome: Rutgers Alcohol Problem Index; N = ", N_rutgers_3, sep=""), escape = FALSE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD_position"))  

ss_tab %>%
  mutate(parameter = as.character(row.names(.))) %>%
  select(parameter, everything()) %>%
  kable(booktabs = TRUE, align = c('c','c','c','c','c','c','c'), caption = paste("Outcome: Rutgers Alcohol Problem Index; N = ", N_rutgers_3, sep="")) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD_position", "scale_down")) 
```


\newpage
# Outcome: HED

## Injunctive Drinking Norms

```{r, echo = FALSE, message = FALSE, warning = FALSE}
fit_HED_1 <- geem(HED ~ sex + race + age + baseline_HED + baseline_social_desirability + baseline_impulsivity + lifestress 
                      + injunctive_workplace_norms, 
                  data = dat_analysis, id = ParticipantID, waves = time, corstr = "exchangeable", family = "quasipoisson")

outfit_HED_1 <- FormatGEEOutput(fit_HED_1)
N_HED_1 <- length(setdiff(unique(dat_analysis$ParticipantID), fit_HED_1$dropped))
```

```{r, echo = FALSE, message = FALSE, warning = FALSE}
fit_HED_2 <- geem(HED ~ sex + race + age + baseline_HED + baseline_social_desirability + baseline_impulsivity + lifestress
                     + time + injunctive_workplace_norms + injunctive_workplace_norms:time, 
                  data = dat_analysis, id = ParticipantID, waves = time, corstr = "exchangeable", family = "quasipoisson")

outfit_HED_2 <- FormatGEEOutput(fit_HED_2)
N_HED_2 <- length(setdiff(unique(dat_analysis$ParticipantID), fit_HED_2$dropped))
```



```{r, echo = FALSE, message = FALSE, warning = FALSE}
fit_HED_3 <- geem(HED ~ sex + race + age 
                                + baseline_HED + baseline_social_desirability + baseline_impulsivity + lifestress
                                + time + injunctive_workplace_norms + DASS + injunctive_workplace_norms:DASS
                                + injunctive_workplace_norms:time + DASS:time + injunctive_workplace_norms:DASS:time, 
                  data = dat_analysis, id = ParticipantID, waves = time, corstr = "exchangeable", family = "quasipoisson")

outfit_HED_3 <- FormatGEEOutput(fit_HED_3)
N_HED_3 <- length(setdiff(unique(dat_analysis$ParticipantID), fit_HED_3$dropped))

# Calculate effects at early onboarding phase
Lmat_low <- as.matrix(c(0,0,0,0, # intercept, sex, race, age
                        0,0,0,0, # end with lifestress
                        # END: control variables
                        0,1,0,-1,
                        0,0,0))

Lmat_mod <- as.matrix(c(0,0,0,0, # intercept, sex, race, age
                        0,0,0,0, # end with lifestress
                        # END: control variables
                        0,1,0,0,
                        0,0,0))

Lmat_hig <- as.matrix(c(0,0,0,0, # intercept, sex, race, age
                        0,0,0,0, # end with lifestress
                        # END: control variables
                        0,1,0,1,
                        0,0,0))

Lmat_low <- t(Lmat_low)
Lmat_mod <- t(Lmat_mod)
Lmat_hig <- t(Lmat_hig)

ss_low <- GetSS(use_this_model = fit_HED_3, L = Lmat_low)
ss_mod <- GetSS(use_this_model = fit_HED_3, L = Lmat_mod)
ss_hig <- GetSS(use_this_model = fit_HED_3, L = Lmat_hig)

ss_tab <- rbind(ss_low, ss_mod, ss_hig)
row.names(ss_tab) <- c("At early onboarding phase: effect of norms at low DASS",
                       "At early onboarding phase: effect of norms at moderate DASS",
                       "At early onboarding phase: effect of norms at high DASS")
```

```{r, echo = FALSE, message = FALSE, warning = FALSE}
outfit_HED_1 %>%
  mutate(parameter = as.character(row.names(.))) %>%
  mutate(parameter = gsub("_"," ", .data[["parameter"]])) %>%
  mutate(parameter = gsub(":"," x ", .data[["parameter"]])) %>%
  select(parameter, everything()) %>%
  mutate_all(linebreak) %>%
  kable(booktabs = TRUE, align = c('c','c','c','c'),
        col.names = linebreak(c("Parameter","Estimates","SE","p-value"), align = "c"),
        caption = paste("Outcome: No. of Days in the Past Month with Heavy Episodic Drinking; N = ", N_HED_1, sep=""), escape = FALSE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD_position"))  

outfit_HED_2 %>%
  mutate(parameter = as.character(row.names(.))) %>%
  select(parameter, everything()) %>%
  mutate(parameter = gsub("_"," ", .data[["parameter"]])) %>%
  mutate(parameter = gsub(":"," x ", .data[["parameter"]])) %>%
  mutate_all(linebreak) %>%
  kable(booktabs = TRUE, align = c('c','c','c','c'),
        col.names = linebreak(c("Parameter","Estimates","SE","p-value"), align = "c"),
        caption = paste("Outcome: No. of Days in the Past Month with Heavy Episodic Drinking; N = ", N_HED_2, sep=""), escape = FALSE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD_position"))  

outfit_rutgers_3 %>%
  mutate(parameter = as.character(row.names(.))) %>%
  select(parameter, everything()) %>%
  mutate(parameter = gsub("_"," ", .data[["parameter"]])) %>%
  mutate(parameter = gsub(":"," x ", .data[["parameter"]])) %>%
  mutate_all(linebreak) %>%
  kable(booktabs = TRUE, align = c('c','c','c','c'),
        col.names = linebreak(c("Parameter","Estimates","SE","p-value"), align = "c"),
        caption = paste("Outcome: No. of Days in the Past Month with Heavy Episodic Drinking; N = ", N_rutgers_3, sep=""), escape = FALSE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD_position"))  

ss_tab %>%
  mutate(parameter = as.character(row.names(.))) %>%
  select(parameter, everything()) %>%
  kable(booktabs = TRUE, align = c('c','c','c','c','c','c','c'), caption = paste("Outcome: No. of Days in the Past Month with Heavy Episodic Drinking; N = ", N_rutgers_3, sep="")) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD_position", "scale_down")) 
```



\newpage
## Descriptive Drinking Norms

```{r, echo = FALSE, message = FALSE, warning = FALSE}
fit_HED_1 <- geem(HED ~ sex + race + age + baseline_HED + baseline_social_desirability + baseline_impulsivity + lifestress 
                      + descriptive_workplace_norms, 
                  data = dat_analysis, id = ParticipantID, waves = time, corstr = "exchangeable", family = "quasipoisson")

outfit_HED_1 <- FormatGEEOutput(fit_HED_1)
N_HED_1 <- length(setdiff(unique(dat_analysis$ParticipantID), fit_HED_1$dropped))
```

```{r, echo = FALSE, message = FALSE, warning = FALSE}
fit_HED_2 <- geem(HED ~ sex + race + age + baseline_HED + baseline_social_desirability + baseline_impulsivity + lifestress
                     + time + descriptive_workplace_norms + descriptive_workplace_norms:time, 
                  data = dat_analysis, id = ParticipantID, waves = time, corstr = "exchangeable", family = "quasipoisson")

outfit_HED_2 <- FormatGEEOutput(fit_HED_2)
N_HED_2 <- length(setdiff(unique(dat_analysis$ParticipantID), fit_HED_2$dropped))
```


```{r, echo = FALSE, message = FALSE, warning = FALSE}
fit_HED_3 <- geem(HED ~ sex + race + age 
                                + baseline_HED + baseline_social_desirability + baseline_impulsivity + lifestress
                                + time + descriptive_workplace_norms + DASS + descriptive_workplace_norms:DASS
                                + descriptive_workplace_norms:time + DASS:time + descriptive_workplace_norms:DASS:time, 
                  data = dat_analysis, id = ParticipantID, waves = time, corstr = "exchangeable", family = "quasipoisson")

outfit_HED_3 <- FormatGEEOutput(fit_HED_3)
N_HED_3 <- length(setdiff(unique(dat_analysis$ParticipantID), fit_HED_3$dropped))

# Calculate effects at early onboarding phase
Lmat_low <- as.matrix(c(0,0,0,0, # intercept, sex, race, age
                        0,0,0,0, # end with lifestress
                        # END: control variables
                        0,1,0,-1,
                        0,0,0))

Lmat_mod <- as.matrix(c(0,0,0,0, # intercept, sex, race, age
                        0,0,0,0, # end with lifestress
                        # END: control variables
                        0,1,0,0,
                        0,0,0))

Lmat_hig <- as.matrix(c(0,0,0,0, # intercept, sex, race, age
                        0,0,0,0, # end with lifestress
                        # END: control variables
                        0,1,0,1,
                        0,0,0))

Lmat_low <- t(Lmat_low)
Lmat_mod <- t(Lmat_mod)
Lmat_hig <- t(Lmat_hig)

ss_low <- GetSS(use_this_model = fit_HED_3, L = Lmat_low)
ss_mod <- GetSS(use_this_model = fit_HED_3, L = Lmat_mod)
ss_hig <- GetSS(use_this_model = fit_HED_3, L = Lmat_hig)

ss_tab <- rbind(ss_low, ss_mod, ss_hig)
row.names(ss_tab) <- c("At early onboarding phase: effect of norms at low DASS",
                       "At early onboarding phase: effect of norms at moderate DASS",
                       "At early onboarding phase: effect of norms at high DASS")
```


```{r, echo = FALSE, message = FALSE, warning = FALSE}
outfit_HED_1 %>%
  mutate(parameter = as.character(row.names(.))) %>%
  mutate(parameter = gsub("_"," ", .data[["parameter"]])) %>%
  mutate(parameter = gsub(":"," x ", .data[["parameter"]])) %>%
  select(parameter, everything()) %>%
  mutate_all(linebreak) %>%
  kable(booktabs = TRUE, align = c('c','c','c','c'),
        col.names = linebreak(c("Parameter","Estimates","SE","p-value"), align = "c"),
        caption = paste("Outcome: No. of Days in the Past Month with Heavy Episodic Drinking; N = ", N_HED_1, sep=""), escape = FALSE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD_position"))  

outfit_HED_2 %>%
  mutate(parameter = as.character(row.names(.))) %>%
  select(parameter, everything()) %>%
  mutate(parameter = gsub("_"," ", .data[["parameter"]])) %>%
  mutate(parameter = gsub(":"," x ", .data[["parameter"]])) %>%
  mutate_all(linebreak) %>%
  kable(booktabs = TRUE, align = c('c','c','c','c'),
        col.names = linebreak(c("Parameter","Estimates","SE","p-value"), align = "c"),
        caption = paste("Outcome: No. of Days in the Past Month with Heavy Episodic Drinking; N = ", N_HED_2, sep=""), escape = FALSE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD_position"))  

outfit_rutgers_3 %>%
  mutate(parameter = as.character(row.names(.))) %>%
  select(parameter, everything()) %>%
  mutate(parameter = gsub("_"," ", .data[["parameter"]])) %>%
  mutate(parameter = gsub(":"," x ", .data[["parameter"]])) %>%
  mutate_all(linebreak) %>%
  kable(booktabs = TRUE, align = c('c','c','c','c'),
        col.names = linebreak(c("Parameter","Estimates","SE","p-value"), align = "c"),
        caption = paste("Outcome: No. of Days in the Past Month with Heavy Episodic Drinking; N = ", N_rutgers_3, sep=""), escape = FALSE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD_position"))  

ss_tab %>%
  mutate(parameter = as.character(row.names(.))) %>%
  select(parameter, everything()) %>%
  kable(booktabs = TRUE, align = c('c','c','c','c','c','c','c'), caption = paste("Outcome: No. of Days in the Past Month with Heavy Episodic Drinking; N = ", N_rutgers_3, sep="")) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD_position", "scale_down")) 
```














