---
title: "Analysis: Part One"
author: 
date: '`r format(Sys.Date(), "%B %d, %Y")`'
geometry: margin=1in
output: 
  pdf_document:
    number_sections: TRUE
---


```{r global_options, include=FALSE}
knitr::opts_chunk$set(tidy = TRUE)
knitr::opts_chunk$set(fig.pos = 'H')
```


```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(rmarkdown)
library(knitr)
library(kableExtra)
```


```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(dplyr)
library(geeM)
path_output_data <- Sys.getenv("path_output_data")

# Read in functions for data analysis
source("analysis-utils.R")

# Read in data
dat_baseline_analysis <- read.csv(file.path(path_output_data, "dat_baseline_analysis.csv"), header = TRUE)
dat_screener_analysis <- read.csv(file.path(path_output_data, "dat_screener_analysis.csv"), header = TRUE)
dat_wnw_analysis <- read.csv(file.path(path_output_data, "dat_wnw_analysis.csv"), header = TRUE)

# Center and scale variables
dat_baseline_analysis <- dat_baseline_analysis %>% mutate(across(!c("ParticipantID"), scale))
dat_screener_analysis <- dat_screener_analysis %>% mutate(across(!c("ParticipantID","sex","race"), scale))
dat_wnw_analysis_0 <- dat_wnw_analysis %>% filter(time==0) %>% mutate(across(!c("ParticipantID","time","survey_timepoint","CASEID","HED","rutgers"), scale))
dat_wnw_analysis_1 <- dat_wnw_analysis %>% filter(time==1) %>% mutate(across(!c("ParticipantID","time","survey_timepoint","CASEID","HED","rutgers"), scale))
dat_wnw_analysis <- rbind(dat_wnw_analysis_0, dat_wnw_analysis_1)
dat_wnw_analysis <- dat_wnw_analysis %>% arrange(ParticipantID, time)
remove(dat_wnw_analysis_0, dat_wnw_analysis_1)

# Merge datasets into one data frame
dat_analysis <- left_join(x = dat_wnw_analysis, y = dat_screener_analysis, by = "ParticipantID")
dat_analysis <- left_join(x = dat_analysis, y = dat_baseline_analysis, by = "ParticipantID")
dat_analysis <- dat_analysis %>% select(colnames(dat_screener_analysis), colnames(dat_baseline_analysis), everything())
```

# Null Hypotheses

* H1a: More permissive peer drinking norms are **not** associated with an increase in alcohol misuse among young adults transitioning from college to work
* H1b: Role overload is **not** associated with an increase in alcohol misuse among young adults transitioning from college to work.
* H5: The effect of drinking norms on alcohol misuse does **not** intensify over time.

# Summary of Results

## Using perceived injunctive work place drinking norms

| Null Hypothesis        | HED  (see Table 3) | RAPI (see Table 11) |
|:---------------|:-------------:|:-------------:|
| H1a                          | _not rejected_ | **rejected** |
| H1b (Qualitative Role Overload)   |  **rejected**  | **rejected** |
| H1b (Quantitative Role Overload)  |  **rejected**  | _not rejected_ (marginally significant) |
| H5                           | _not rejected_ |  _not rejected_  |

| Null Hypothesis        | HED  (see Table 5) | RAPI (see Table 13) |
|:---------------|:-------------:|:-------------:|
| H1a                          | _not rejected_ | **rejected** |
| H1b (Qualitative Role Overload)   |  **rejected**  | **rejected** |
| H1b (Quantitative Role Overload)  |  **rejected**  | _not rejected_ (marginally significant) |
| H5                           | _not rejected_ |  _not rejected_  |

| Null Hypothesis        | HED  (see Table 6) | RAPI (see Table 14) |
|:---------------|:-------------:|:-------------:|
| H1a                          | _not rejected_ | **rejected** |
| H1b (Qualitative Role Overload)   |  **rejected**  | **rejected** |
| H1b (Quantitative Role Overload)  |  **rejected**  | _not rejected_ (marginally significant) |
| H5                           | _not rejected_ |  _not rejected_  |

\newpage

## Using perceived descriptive work place drinking norms


| Null Hypothesis        | HED (see Table 4) | RAPI (see Table 12) |
|:---------------|:-------------:|:-------------:|
| H1a                           | _not rejected_  | **rejected** |
| H1b (Qualitative Role Overload)    |  **rejected**   |  **rejected** |
| H1b (Quantitative Role Overload)   |  **rejected**   |  _not rejected_ (marginally significant) |
| H5                            | _not rejected_  |  _not rejected_  |

| Null Hypothesis        | HED (see Table 7) | RAPI (see Table 15) |
|:---------------|:-------------:|:-------------:|
| H1a                           | _not rejected_  | **rejected** |
| H1b (Qualitative Role Overload)    |  **rejected**   |  **rejected** |
| H1b (Quantitative Role Overload)   |  **rejected**   |  **rejected** |
| H5                            | _not rejected_  |  _not rejected_  |

| Null Hypothesis        | HED (see Table 8) | RAPI (see Table 16) |
|:---------------|:-------------:|:-------------:|
| H1a                           | _not rejected_  | **rejected** |
| H1b (Qualitative Role Overload)    |  **rejected**   |  **rejected** |
| H1b (Quantitative Role Overload)   |  **rejected**   |  _not rejected_ (marginally significant) |
| H5                            | _not rejected_  |  _not rejected_  |


# Drinking Norms Variables

* Perceived injunctive work place drinking norms - mean of wnw111 and wnw114 where

  - wnw111: Please indicate the degree to which these others, not you, disapprove/approve of the various patterns of alcohol consumption described. What is the extent you believe: Your closest friends at work would approve/disapprove were you to have 1-2 servings of alcohol within an hour of coming to work?
  - wnw114: Please indicate the degree to which these others, not you, disapprove/approve of the various patterns of alcohol consumption described. What is the extent you believe: Your closest friends and colleagues at work would approve/disapprove were you to have 1-2 servings of alcohol at work?

* Perceived descriptive work place drinking norms - mean of wnw116 and wnw117 where

  - wnw116: In the past month, how many of your closest friends and colleagues at work: Consumed 1-2 servings of alcohol within an hour before starting work?
  - wnw117: In the past month, how many of your closest friends and colleagues at work: Consumed at least one serving of alcohol during the work day?

\newpage 

# Dependent Variable: HED

```{r, echo = FALSE, message = FALSE, warning = FALSE}
fit_HED_1 <- geem(HED ~ sex + race + age + baseline_HED + baseline_social_desirability + baseline_impulsivity + lifestress + time, 
                  data = dat_analysis, id = ParticipantID, waves = time, corstr = "exchangeable", family = "quasipoisson")


fit_HED_2 <- geem(HED ~ sex + race + age + baseline_HED + baseline_social_desirability + baseline_impulsivity + lifestress + time
                  + qualitative_role_overload + quantitative_role_overload + injunctive_workplace_norms 
                  + time:qualitative_role_overload + time:quantitative_role_overload + time:injunctive_workplace_norms, 
                  data = dat_analysis, id = ParticipantID, waves = time, corstr = "exchangeable", family = "quasipoisson")

fit_HED_3 <- geem(HED ~ sex + race + age + baseline_HED + baseline_social_desirability + baseline_impulsivity + lifestress + time
                  + qualitative_role_overload + quantitative_role_overload + descriptive_workplace_norms 
                  + time:qualitative_role_overload + time:quantitative_role_overload + time:descriptive_workplace_norms, 
                  data = dat_analysis, id = ParticipantID, waves = time, corstr = "exchangeable", family = "quasipoisson")

fit_HED_4 <- geem(HED ~ sex + race + age + baseline_HED + baseline_social_desirability + baseline_impulsivity + lifestress + time
                  + qualitative_role_overload + quantitative_role_overload + wnw114 
                  + time:qualitative_role_overload + time:quantitative_role_overload + time:wnw114, 
                  data = dat_analysis, id = ParticipantID, waves = time, corstr = "exchangeable", family = "quasipoisson")

fit_HED_5 <- geem(HED ~ sex + race + age + baseline_HED + baseline_social_desirability + baseline_impulsivity + lifestress + time
                  + qualitative_role_overload + quantitative_role_overload + wnw111 
                  + time:qualitative_role_overload + time:quantitative_role_overload + time:wnw111, 
                  data = dat_analysis, id = ParticipantID, waves = time, corstr = "exchangeable", family = "quasipoisson")

fit_HED_6 <- geem(HED ~ sex + race + age + baseline_HED + baseline_social_desirability + baseline_impulsivity + lifestress + time
                  + qualitative_role_overload + quantitative_role_overload + wnw117 
                  + time:qualitative_role_overload + time:quantitative_role_overload + time:wnw117, 
                  data = dat_analysis, id = ParticipantID, waves = time, corstr = "exchangeable", family = "quasipoisson")

fit_HED_7 <- geem(HED ~ sex + race + age + baseline_HED + baseline_social_desirability + baseline_impulsivity + lifestress + time
                  + qualitative_role_overload + quantitative_role_overload + wnw116 
                  + time:qualitative_role_overload + time:quantitative_role_overload + time:wnw116, 
                  data = dat_analysis, id = ParticipantID, waves = time, corstr = "exchangeable", family = "quasipoisson")
```


```{r, echo = FALSE, message = FALSE, warning = FALSE}
outfit_HED_1 <- FormatGEEOutput(fit_HED_1)
outfit_HED_2 <- FormatGEEOutput(fit_HED_2)
outfit_HED_3 <- FormatGEEOutput(fit_HED_3)
outfit_HED_4 <- FormatGEEOutput(fit_HED_4)
outfit_HED_5 <- FormatGEEOutput(fit_HED_5)
outfit_HED_6 <- FormatGEEOutput(fit_HED_6)
outfit_HED_7 <- FormatGEEOutput(fit_HED_7)

N_HED_1 <- length(setdiff(unique(dat_analysis$ParticipantID), fit_HED_1$dropped))
N_HED_2 <- length(setdiff(unique(dat_analysis$ParticipantID), fit_HED_2$dropped))
N_HED_3 <- length(setdiff(unique(dat_analysis$ParticipantID), fit_HED_3$dropped))
N_HED_4 <- length(setdiff(unique(dat_analysis$ParticipantID), fit_HED_4$dropped))
N_HED_5 <- length(setdiff(unique(dat_analysis$ParticipantID), fit_HED_5$dropped))
N_HED_6 <- length(setdiff(unique(dat_analysis$ParticipantID), fit_HED_6$dropped))
N_HED_7 <- length(setdiff(unique(dat_analysis$ParticipantID), fit_HED_7$dropped))
```


```{r, echo = FALSE, message = FALSE, warning = FALSE}
outfit_HED_1 %>%
  mutate(parameter = as.character(row.names(.))) %>%
  mutate(parameter = gsub("_"," ", .data[["parameter"]])) %>%
  mutate(parameter = gsub(":"," x ", .data[["parameter"]])) %>%
  select(parameter, everything()) %>%
  mutate_all(linebreak) %>%
  kable(booktabs = TRUE, align = c('c','c','c','c'),
        col.names = linebreak(c("Parameter","Estimates","SE","p-value"), align = "c"),
        caption = paste("Outcome: Count of past-month heavy drinking days; N = ", N_HED_1, sep=""), escape = FALSE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD_position"))  

outfit_HED_2 %>%
  mutate(parameter = as.character(row.names(.))) %>%
  select(parameter, everything()) %>%
  mutate(parameter = gsub("_"," ", .data[["parameter"]])) %>%
  mutate(parameter = gsub(":"," x ", .data[["parameter"]])) %>%
  mutate_all(linebreak) %>%
  kable(booktabs = TRUE, align = c('c','c','c','c'),
        col.names = linebreak(c("Parameter","Estimates","SE","p-value"), align = "c"),
        caption = paste("Outcome: Count of past-month heavy drinking days; N = ", N_HED_2, sep=""), escape = FALSE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD_position"))  

outfit_HED_3 %>%
  mutate(parameter = as.character(row.names(.))) %>%
  select(parameter, everything()) %>%
  mutate(parameter = gsub("_"," ", .data[["parameter"]])) %>%
  mutate(parameter = gsub(":"," x ", .data[["parameter"]])) %>%
  mutate_all(linebreak) %>%
  kable(booktabs = TRUE, align = c('c','c','c','c'),
        col.names = linebreak(c("Parameter","Estimates","SE","p-value"), align = "c"),
        caption = paste("Outcome: Count of past-month heavy drinking days; N = ", N_HED_3, sep=""), escape = FALSE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD_position"))  

outfit_HED_4 %>%
  mutate(parameter = as.character(row.names(.))) %>%
  select(parameter, everything()) %>%
  mutate(parameter = gsub("_"," ", .data[["parameter"]])) %>%
  mutate(parameter = gsub(":"," x ", .data[["parameter"]])) %>%
  mutate_all(linebreak) %>%
  kable(booktabs = TRUE, align = c('c','c','c','c'),
        col.names = linebreak(c("Parameter","Estimates","SE","p-value"), align = "c"),
        caption = paste("Outcome: Count of past-month heavy drinking days; N = ", N_HED_4, sep=""), escape = FALSE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD_position"))  

outfit_HED_5 %>%
  mutate(parameter = as.character(row.names(.))) %>%
  select(parameter, everything()) %>%
  mutate(parameter = gsub("_"," ", .data[["parameter"]])) %>%
  mutate(parameter = gsub(":"," x ", .data[["parameter"]])) %>%
  mutate_all(linebreak) %>%
  kable(booktabs = TRUE, align = c('c','c','c','c'),
        col.names = linebreak(c("Parameter","Estimates","SE","p-value"), align = "c"),
        caption = paste("Outcome: Count of past-month heavy drinking days; N = ", N_HED_5, sep=""), escape = FALSE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD_position"))  

outfit_HED_6 %>%
  mutate(parameter = as.character(row.names(.))) %>%
  select(parameter, everything()) %>%
  mutate(parameter = gsub("_"," ", .data[["parameter"]])) %>%
  mutate(parameter = gsub(":"," x ", .data[["parameter"]])) %>%
  mutate_all(linebreak) %>%
  kable(booktabs = TRUE, align = c('c','c','c','c'),
        col.names = linebreak(c("Parameter","Estimates","SE","p-value"), align = "c"),
        caption = paste("Outcome: Count of past-month heavy drinking days; N = ", N_HED_6, sep=""), escape = FALSE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD_position"))  

outfit_HED_7 %>%
  mutate(parameter = as.character(row.names(.))) %>%
  select(parameter, everything()) %>%
  mutate(parameter = gsub("_"," ", .data[["parameter"]])) %>%
  mutate(parameter = gsub(":"," x ", .data[["parameter"]])) %>%
  mutate_all(linebreak) %>%
  kable(booktabs = TRUE, align = c('c','c','c','c'),
        col.names = linebreak(c("Parameter","Estimates","SE","p-value"), align = "c"),
        caption = paste("Outcome: Count of past-month heavy drinking days; N = ", N_HED_7, sep=""), escape = FALSE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD_position"))  
```

\newpage

# Dependent Variable: RAPI

```{r, echo = FALSE, message = FALSE, warning = FALSE}
fit_rutgers_1 <- geem(rutgers ~ sex + race + age + baseline_rutgers + baseline_social_desirability + baseline_impulsivity + lifestress + time, 
                  data = dat_analysis, id = ParticipantID, waves = time, corstr = "exchangeable", family = "quasipoisson")


fit_rutgers_2 <- geem(rutgers ~ sex + race + age + baseline_rutgers + baseline_social_desirability + baseline_impulsivity + lifestress + time
                  + qualitative_role_overload + quantitative_role_overload + injunctive_workplace_norms 
                  + time:qualitative_role_overload + time:quantitative_role_overload + time:injunctive_workplace_norms, 
                  data = dat_analysis, id = ParticipantID, waves = time, corstr = "exchangeable", family = "quasipoisson")

fit_rutgers_3 <- geem(rutgers ~ sex + race + age + baseline_rutgers + baseline_social_desirability + baseline_impulsivity + lifestress + time
                  + qualitative_role_overload + quantitative_role_overload + descriptive_workplace_norms 
                  + time:qualitative_role_overload + time:quantitative_role_overload + time:descriptive_workplace_norms, 
                  data = dat_analysis, id = ParticipantID, waves = time, corstr = "exchangeable", family = "quasipoisson")

fit_rutgers_4 <- geem(rutgers ~ sex + race + age + baseline_rutgers + baseline_social_desirability + baseline_impulsivity + lifestress + time
                  + qualitative_role_overload + quantitative_role_overload + wnw114 
                  + time:qualitative_role_overload + time:quantitative_role_overload + time:wnw114, 
                  data = dat_analysis, id = ParticipantID, waves = time, corstr = "exchangeable", family = "quasipoisson")

fit_rutgers_5 <- geem(rutgers ~ sex + race + age + baseline_rutgers + baseline_social_desirability + baseline_impulsivity + lifestress + time
                  + qualitative_role_overload + quantitative_role_overload + wnw111 
                  + time:qualitative_role_overload + time:quantitative_role_overload + time:wnw111, 
                  data = dat_analysis, id = ParticipantID, waves = time, corstr = "exchangeable", family = "quasipoisson")

fit_rutgers_6 <- geem(rutgers ~ sex + race + age + baseline_rutgers + baseline_social_desirability + baseline_impulsivity + lifestress + time
                  + qualitative_role_overload + quantitative_role_overload + wnw117 
                  + time:qualitative_role_overload + time:quantitative_role_overload + time:wnw117, 
                  data = dat_analysis, id = ParticipantID, waves = time, corstr = "exchangeable", family = "quasipoisson")

fit_rutgers_7 <- geem(rutgers ~ sex + race + age + baseline_rutgers + baseline_social_desirability + baseline_impulsivity + lifestress + time
                  + qualitative_role_overload + quantitative_role_overload + wnw116 
                  + time:qualitative_role_overload + time:quantitative_role_overload + time:wnw116, 
                  data = dat_analysis, id = ParticipantID, waves = time, corstr = "exchangeable", family = "quasipoisson")
```


```{r, echo = FALSE, message = FALSE, warning = FALSE}
outfit_rutgers_1 <- FormatGEEOutput(fit_rutgers_1)
outfit_rutgers_2 <- FormatGEEOutput(fit_rutgers_2)
outfit_rutgers_3 <- FormatGEEOutput(fit_rutgers_3)
outfit_rutgers_4 <- FormatGEEOutput(fit_rutgers_4)
outfit_rutgers_5 <- FormatGEEOutput(fit_rutgers_5)
outfit_rutgers_6 <- FormatGEEOutput(fit_rutgers_6)
outfit_rutgers_7 <- FormatGEEOutput(fit_rutgers_7)

N_rutgers_1 <- length(setdiff(unique(dat_analysis$ParticipantID), fit_rutgers_1$dropped))
N_rutgers_2 <- length(setdiff(unique(dat_analysis$ParticipantID), fit_rutgers_2$dropped))
N_rutgers_3 <- length(setdiff(unique(dat_analysis$ParticipantID), fit_rutgers_3$dropped))
N_rutgers_4 <- length(setdiff(unique(dat_analysis$ParticipantID), fit_rutgers_4$dropped))
N_rutgers_5 <- length(setdiff(unique(dat_analysis$ParticipantID), fit_rutgers_5$dropped))
N_rutgers_6 <- length(setdiff(unique(dat_analysis$ParticipantID), fit_rutgers_6$dropped))
N_rutgers_7 <- length(setdiff(unique(dat_analysis$ParticipantID), fit_rutgers_7$dropped))
```


```{r, echo = FALSE, message = FALSE, warning = FALSE}
outfit_rutgers_1 %>%
  mutate(parameter = as.character(row.names(.))) %>%
  mutate(parameter = gsub("_"," ", .data[["parameter"]])) %>%
  mutate(parameter = gsub(":"," x ", .data[["parameter"]])) %>%
  select(parameter, everything()) %>%
  mutate_all(linebreak) %>%
  kable(booktabs = TRUE, align = c('c','c','c','c'),
        col.names = linebreak(c("Parameter","Estimates","SE","p-value"), align = "c"),
        caption = paste("Outcome: Rutgers Alcohol Problem Index; N = ", N_rutgers_1, sep=""), escape = FALSE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD_position"))  

outfit_rutgers_2 %>%
  mutate(parameter = as.character(row.names(.))) %>%
  select(parameter, everything()) %>%
  mutate(parameter = gsub("_"," ", .data[["parameter"]])) %>%
  mutate(parameter = gsub(":"," x ", .data[["parameter"]])) %>%
  mutate_all(linebreak) %>%
  kable(booktabs = TRUE, align = c('c','c','c','c'),
        col.names = linebreak(c("Parameter","Estimates","SE","p-value"), align = "c"),
        caption = paste("Outcome: Rutgers Alcohol Problem Index; N = ", N_rutgers_2, sep=""), escape = FALSE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD_position"))  

outfit_rutgers_3 %>%
  mutate(parameter = as.character(row.names(.))) %>%
  select(parameter, everything()) %>%
  mutate(parameter = gsub("_"," ", .data[["parameter"]])) %>%
  mutate(parameter = gsub(":"," x ", .data[["parameter"]])) %>%
  mutate_all(linebreak) %>%
  kable(booktabs = TRUE, align = c('c','c','c','c'),
        col.names = linebreak(c("Parameter","Estimates","SE","p-value"), align = "c"),
        caption = paste("Outcome: Rutgers Alcohol Problem Index; N = ", N_rutgers_3, sep=""), escape = FALSE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD_position"))  

outfit_rutgers_4 %>%
  mutate(parameter = as.character(row.names(.))) %>%
  select(parameter, everything()) %>%
  mutate(parameter = gsub("_"," ", .data[["parameter"]])) %>%
  mutate(parameter = gsub(":"," x ", .data[["parameter"]])) %>%
  mutate_all(linebreak) %>%
  kable(booktabs = TRUE, align = c('c','c','c','c'),
        col.names = linebreak(c("Parameter","Estimates","SE","p-value"), align = "c"),
        caption = paste("Outcome: Rutgers Alcohol Problem Index; N = ", N_rutgers_4, sep=""), escape = FALSE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD_position"))  

outfit_rutgers_5 %>%
  mutate(parameter = as.character(row.names(.))) %>%
  select(parameter, everything()) %>%
  mutate(parameter = gsub("_"," ", .data[["parameter"]])) %>%
  mutate(parameter = gsub(":"," x ", .data[["parameter"]])) %>%
  mutate_all(linebreak) %>%
  kable(booktabs = TRUE, align = c('c','c','c','c'),
        col.names = linebreak(c("Parameter","Estimates","SE","p-value"), align = "c"),
        caption = paste("Outcome: Rutgers Alcohol Problem Index; N = ", N_rutgers_5, sep=""), escape = FALSE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD_position"))  

outfit_rutgers_6 %>%
  mutate(parameter = as.character(row.names(.))) %>%
  select(parameter, everything()) %>%
  mutate(parameter = gsub("_"," ", .data[["parameter"]])) %>%
  mutate(parameter = gsub(":"," x ", .data[["parameter"]])) %>%
  mutate_all(linebreak) %>%
  kable(booktabs = TRUE, align = c('c','c','c','c'),
        col.names = linebreak(c("Parameter","Estimates","SE","p-value"), align = "c"),
        caption = paste("Outcome: Rutgers Alcohol Problem Index; N = ", N_rutgers_6, sep=""), escape = FALSE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD_position"))  

outfit_rutgers_7 %>%
  mutate(parameter = as.character(row.names(.))) %>%
  select(parameter, everything()) %>%
  mutate(parameter = gsub("_"," ", .data[["parameter"]])) %>%
  mutate(parameter = gsub(":"," x ", .data[["parameter"]])) %>%
  mutate_all(linebreak) %>%
  kable(booktabs = TRUE, align = c('c','c','c','c'),
        col.names = linebreak(c("Parameter","Estimates","SE","p-value"), align = "c"),
        caption = paste("Outcome: Rutgers Alcohol Problem Index; N = ", N_rutgers_7, sep=""), escape = FALSE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD_position"))  
```







