---
title: "Tests of Homogeneity"
author: 
date: '`r format(Sys.Date(), "%B %d, %Y")`'
geometry: margin=1in
output: 
  pdf_document:
    number_sections: TRUE
---


```{r global_options, include=FALSE}
knitr::opts_chunk$set(tidy = TRUE)
knitr::opts_chunk$set(fig.pos = 'H')
```

# Overview

Conduct Chi-squared tests (for binary variables) or Kolmogorov-Smirnov tests (for continuous variables) to test for homogeneity across two samples. The two samples are:

1. Participants who were **included** in analyses having RAPI as the outcome of interest 
1. Participants who were **excluded** in analyses having RAPI as the outcome of interest 

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(rmarkdown)
library(knitr)
library(kableExtra)
set.seed(55441133)
```

# Results for RAPI as outcome of interest

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(dplyr)
library(geeM)
library(MuMIn)
path_output_data <- Sys.getenv("path_output_data")

# Read in functions for data analysis
source("analysis-utils.R")

# Read in data
dat_baseline_analysis <- read.csv(file.path(path_output_data, "dat_baseline_analysis.csv"), header = TRUE)
dat_screener_analysis <- read.csv(file.path(path_output_data, "dat_screener_analysis.csv"), header = TRUE)
dat_wnw_analysis <- read.csv(file.path(path_output_data, "dat_wnw_analysis.csv"), header = TRUE)

# Merge datasets into one data frame
dat_wnw_analysis <- dat_wnw_analysis %>% arrange(ParticipantID, time)
dat_analysis <- left_join(x = dat_wnw_analysis, y = dat_screener_analysis, by = "ParticipantID")
dat_analysis <- left_join(x = dat_analysis, y = dat_baseline_analysis, by = "ParticipantID")
dat_analysis <- dat_analysis %>% select(colnames(dat_screener_analysis), colnames(dat_baseline_analysis), everything())
```

```{r, echo = FALSE, message = FALSE, warning = FALSE}
dat_analysis <- dat_analysis %>%
  filter(baseline_condition!=1) %>%
  filter(condition!=1)
```

```{r, echo = FALSE, message = FALSE, warning = FALSE}
keep_rows <- complete.cases(dat_analysis[, !(colnames(dat_analysis) %in% c("baseline_HED", "HED"))])

dat_sample_complete <- dat_analysis %>% 
  filter(keep_rows)

dat_sample_notcomplete <- dat_analysis %>% 
  filter(!keep_rows)
```


```{r, echo = FALSE, message = FALSE, warning = FALSE}
ids_sample_complete <- unique(dat_sample_complete$ParticipantID)
ids_sample_notcomplete <- unique(dat_sample_notcomplete$ParticipantID)
```


```{r, echo = FALSE, message = FALSE, warning = FALSE}
dat_results_rutgers <- data.frame(variable = NULL, time = NULL, pval = NULL)
```

```{r, echo = FALSE, message = FALSE, warning = FALSE}
covariate <- c("sex")

dat_complete_case <- dat_sample_complete %>% 
  filter(ParticipantID %in% ids_sample_complete) %>%
  select(ParticipantID, all_of(covariate)) %>%
  filter(!duplicated(.)) %>%
  select(all_of(covariate))

dat_with_miss <- dat_sample_notcomplete %>% 
  select(ParticipantID, all_of(covariate)) %>%
  filter(!duplicated(.)) %>%
  select(all_of(covariate))

tab_complete <- table(dat_complete_case)
tab_miss <- table(dat_with_miss)
df_tab_complete <- as.data.frame(tab_complete)
df_tab_miss <- as.data.frame(tab_miss)
colnames(df_tab_complete) <- c("value", "count_complete")
colnames(df_tab_miss) <- c("value", "count_missing")


df_merged <- full_join(x = df_tab_complete, y = df_tab_miss, by = "value")
df_merged <- df_merged[order(df_merged$value),]
df_merged$count_complete <- ifelse(is.na(df_merged$count_complete), 0, df_merged$count_complete)
df_merged$count_missing <- ifelse(is.na(df_merged$count_missing), 0, df_merged$count_missing)
mat <- df_merged[, c("count_complete", "count_missing")]

res <- chisq.test(mat, simulate.p.value = TRUE)

dat_results_tmp <- data.frame(variable = "sex", pval = res[["p.value"]])
dat_results_rutgers <- rbind(dat_results_rutgers, dat_results_tmp)

df_merged_sex <- df_merged
```


```{r, echo = FALSE, message = FALSE, warning = FALSE}
covariate <- c("age")

dat_complete_case <- dat_sample_complete %>% 
  select(ParticipantID, all_of(covariate)) %>%
  filter(!duplicated(.)) %>%
  select(all_of(covariate))

dat_with_miss <- dat_sample_notcomplete %>%
  select(ParticipantID, all_of(covariate)) %>%
  filter(!duplicated(.)) %>%
  select(all_of(covariate))

res <- ks.test(x = dat_complete_case[["age"]], dat_with_miss[["age"]], exact = TRUE)

dat_results_tmp <- data.frame(variable = "age", pval = res[["p.value"]])
dat_results_rutgers <- rbind(dat_results_rutgers, dat_results_tmp)
```



```{r, echo = FALSE, message = FALSE, warning = FALSE}
covariate <- c("race")

dat_complete_case <- dat_sample_complete %>% 
  select(ParticipantID, all_of(covariate)) %>%
  filter(!duplicated(.)) %>%
  select(all_of(covariate))

dat_with_miss <- dat_sample_notcomplete %>% 
  select(ParticipantID, all_of(covariate)) %>%
  filter(!duplicated(.)) %>%
  select(all_of(covariate))

tab_complete <- table(dat_complete_case)
tab_miss <- table(dat_with_miss)
df_tab_complete <- as.data.frame(tab_complete)
df_tab_miss <- as.data.frame(tab_miss)
colnames(df_tab_complete) <- c("value", "count_complete")
colnames(df_tab_miss) <- c("value", "count_missing")


df_merged <- full_join(x = df_tab_complete, y = df_tab_miss, by = "value")
df_merged <- df_merged[order(df_merged$value),]
df_merged$count_complete <- ifelse(is.na(df_merged$count_complete), 0, df_merged$count_complete)
df_merged$count_missing <- ifelse(is.na(df_merged$count_missing), 0, df_merged$count_missing)
mat <- df_merged[, c("count_complete", "count_missing")]

res <- chisq.test(mat, simulate.p.value = TRUE)

dat_results_tmp <- data.frame(variable = "race", pval = res[["p.value"]])
dat_results_rutgers <- rbind(dat_results_rutgers, dat_results_tmp)

df_merged_race <- df_merged
```


```{r, echo = FALSE, message = FALSE, warning = FALSE}
dat_results_rutgers[["pval"]] <- format(round(dat_results_rutgers[["pval"]], 3), nsmall = 3)
```

```{r, echo = FALSE, message = FALSE, warning = FALSE}
colnames(dat_results_rutgers) <- c("Variable", "p")

kable(dat_results_rutgers, 
      booktabs=TRUE, 
      caption = "$H_0:$ There is no difference in the distribution of the variable of interest (Column 1) across the two samples being compared", 
      escape = FALSE) %>%
  kable_styling(position = "center", latex_options = "HOLD_position")
```



```{r, echo = FALSE, message = FALSE, warning = FALSE}
df_merged_sex <- df_merged_sex %>% 
  arrange(desc(value)) %>%
  mutate(value = if_else(value==1, "female", "others"),
         percent_of_complete = 100 * (count_complete/sum(df_merged_sex[["count_complete"]])),
         percent_of_missing = 100 * (count_missing/sum(df_merged_sex[["count_missing"]])))

df_merged_sex <- rbind(df_merged_sex, c(NA, colSums(df_merged_sex[,2:5])))
df_merged_sex[3,1] <- "Grand Total"
df_merged_sex[["percent_of_complete"]] <- format(round(df_merged_sex[["percent_of_complete"]], 3), nsmall = 3)
df_merged_sex[["percent_of_missing"]] <- format(round(df_merged_sex[["percent_of_missing"]], 3), nsmall = 3)
```


```{r, echo = FALSE, message = FALSE, warning = FALSE}
colnames(df_merged_sex) <- c("Category", "Count among included", "Count among excluded", "Percent among included", "Percent among excluded")

kable(df_merged_sex, 
      booktabs=TRUE, 
      caption = "Participants who reported their sex to be female vs. others", 
      escape = FALSE) %>%
  kable_styling(position = "center", latex_options = "HOLD_position")
```

```{r, echo = FALSE, message = FALSE, warning = FALSE}
df_merged_race <- df_merged_race %>% 
  arrange(desc(value)) %>%
  mutate(value = if_else(value==1, "white", "others"),
         percent_of_complete = 100 * (count_complete/sum(df_merged_race[["count_complete"]])),
         percent_of_missing = 100 * (count_missing/sum(df_merged_race[["count_missing"]])))

df_merged_race <- rbind(df_merged_race, c(NA, colSums(df_merged_race[,2:5])))
df_merged_race[3,1] <- "Grand Total"
df_merged_race[["percent_of_complete"]] <- format(round(df_merged_race[["percent_of_complete"]], 3), nsmall = 3)
df_merged_race[["percent_of_missing"]] <- format(round(df_merged_race[["percent_of_missing"]], 3), nsmall = 3)
```


```{r, echo = FALSE, message = FALSE, warning = FALSE}
colnames(df_merged_race) <- c("Category", "Count among included", "Count among excluded", "Percent among included", "Percent among excluded")

kable(df_merged_race, 
      booktabs=TRUE, 
      caption = "Participants who reported their race to be white vs. others", 
      escape = FALSE) %>%
  kable_styling(position = "center", latex_options = "HOLD_position")
```



